make_lineplots_simd_deciles

### 2023-07-12 minos/outcomes/make_lineplots_simd_deciles.Rmd
trying much smaller number of files for sanity

```{python simd deciles, fig.path="plots/"}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline"
tags = "National Average,First,Second,Third,Fourth,Fifth,Sixth,Seventh,Eighth,Ninth,Tenth"
subset_function_strings = "who_alive,who_first_decile,who_second_decile,who_third_decile,who_fourth_decile,who_fifth_decile,who_sixth_decile,who_seventh_decile,who_eigth_decile,who_ninth_decile,who_tenth_decile"
prefix="simd_deciles"
config_mode = "glasgow_scaled"
lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="National Average", v="SF_12", method='nanmean')
```

>>>>

```{python simd deciles, fig.path="plots/"}
# packages need installing in R using py_install("package"). honestly this seems not worth it..
from minos.outcomes.make_lineplots import main as lineplot_main
# define test parameters and run.
directories = "baseline,baseline"#,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline,baseline"
tags = "National Average,First"#,Second,Third,Fourth,Fifth,Sixth,Seventh,Eighth,Ninth,Tenth"
subset_function_strings = "who_alive,who_first_decile"#,who_second_decile,who_third_decile,who_fourth_decile,who_fifth_decile,who_sixth_decile,who_seventh_decile,who_eigth_decile,who_ninth_decile,who_tenth_decile"
prefix="simd_deciles"
config_mode = "glasgow_scaled"
lineplot_main(directories, tags, subset_function_strings, prefix, mode=config_mode, ref="National Average", v="SF_12", method='nanmean')
```
